Graphs of Mice and Men

### 2016-07-01 Paper/Draft.tex
Did some stuff yesterday but did not commit. Also, moved system check

 \usepackage[utf8]{inputenc}
 \usepackage[titletoc]{appendix}
 \usepackage{listings}
 \usepackage{amsmath}
 \usepackage{graphicx}
 \usepackage{float}
 \usepackage{caption}
 \usepackage[export]{adjustbox}
 \usepackage{url}
 \usepackage{subcaption}

 \title{Ontology Matching with word2vec}
 \author{Harmen Prins}

 \begin{document}
 \pagenumbering{gobble}
 \maketitle
 \newpage

@@

 \section*{Summary}
 %TODO Definitions
 %TODO Word index
 %TODO Fix hoofdletters (bv ontology, kb)
 %TODO spelling (database dataset)
 %TODO volgorde bieb (APA?)
 %TODO \caption[DIT DOEN]{te lang}
 \tableofcontents
 \newpage

@@

The Universal Schema uses two steps. Firstly, the system learns embeddings of entities and relations found in text and Knowledge Bases\cite{univeralschema}, see Figure \ref{McCallum_matrix}. Secondly, these embeddings are then used to predict new relations for the knowledge bases. The system finds embeddings such that the embeddings of entities and relations that co-occur are highly similar, see Figure \ref{McCallum_matrix}.

@@

 \begin{figure}[H]
 \centering
 \includegraphics[width=0.8\textwidth]{plots/Skip-Gram}
 \label{Skip-Gram-img}
 \caption[Skip-Gram Model]{The embedding of a row (in pink) is optimized to be close to its context embeddings (in purple) but far away from other embeddings (in red).}
 \end{figure}

@@

 McCallum plans on using these embeddings to predict new intra-knowledge base relations. However, from they keynote it is clear that this technique should work with multiple Knowledge Bases as the Universal Schema is applied to a set of Knowledge Bases including Freebase, knowledge extracted from text and the TAC Knowledge Bases Population Track Dataset. This means that inter-knowledge base relations can also be predicted using the Word Embedding Tensor Factorisation technique.

@@

 \newpage
 \section{Method} 
 This section contains the description of the matching system and experimental setup. It consists of four parts. Firstly, it describes the idea and challenges of implementing the system. Secondly, it describes the data used to test the system. The third part describes all different implementations of the system. The fourth and last part describes the evaluation criteria.

@@

 \newpage
 \subsection{Evaluation}
 The goal of the research is to find an ontology alignment algorithm $A$ and prove that it performs better than current techniques. However, as current techniques may combine many different algorithms and sources of information, maybe such a comparison is not fair, nor is a comparison with individual algorithms as they may be optimised for being combined. So, instead we may want to see if performance is improved when adding $A$ to an ensemble of algorithms $E=(A_1,..,A_n)$.
 \subsubsection{Evaluation methods} \label{EvaluationMethods}
 The evaluation should be done using a performance measure $P(Al,T)$ that takes the alignment an algorithm produces given an ontology and the ground truth. If both the alignment and truth are considered sets of alignments, i.e. $Al=\{a_1,..,a_n\}$ and $T=\{a'_1,..,a'_m\}$, then the True Positives $TP=\{a|a\in Al, a\in T\}$, False Positives $FP=\{a|a\in Al, a\notin T\}$ and False Negatives $FN=\{a|a\in T, a\notin Al\}$ determine the performance of the alignment. The True Negatives do not matter, as there are extremely many, and the goal of ontology matching is to find True Positives. If we only care about True Positives, the Jaccard similarity is a prime candidate for the performance measure.
 \paragraph{}
 The Jaccard similarity is calculated as follows
 \[
 J = \frac{TP}{TP + FP + FN}
 \]
 i.e. the fraction of the true positives over the sum of the true positives and mistakes.
 \paragraph{}
 The Jaccard similarity is a number between 0 and 1, with a higher number being better. Therefore if we compare two alignments, the one which is most similar to the truth, i.e. has a higher Jaccard similarity, is the better one.
 \paragraph{}
 However, if we want to find out if an algorithm improves an ensemble, we calculate the improvement as follows:
 \[
 I = J_{E\cup \{A\}} - J_E
 \]
 where $J_E$ is the Jaccard coefficient of an ensemble $E$.
 To see if an algorithm is useful to an ensemble, the improvement score $I$ has to be \emph{significantly} higher than zero. To check if a score is significant, a statistical significance test will have to be carried out, which works as follows: generate $N$ solutions randomly and score them. Then score the method you want to investigate. If the score is in the top p\%, it is significant, otherwise it is not. In this case the solutions are $E\cup \{R\}$, where $R$ is an algorithm that generates random alignments\cite{fisher1925statistical}.
 \paragraph{}
 It is in principle possible to weigh False Positives and False Negatives differently, but this is not done in practice. To make the results of this study easily comparable to others, equal weights will be used.

@@

 %TODO F measure noteren op pieken. Dan confidence vs F-measure bespreken in interpretation.
 % Wat is de threshold van AML?
 % Extra rij met baseline literal string matcher
 \subsection{Precision versus recall}
  \subsubsection{Mice and men data}
  \begin{figure}[H]
   \centering
   \includegraphics[width=\textwidth]{plots/untrained_ROC}
   \caption[Precision-recall curve untrained mice]{The precision and recall trade-off for the results of the untrained Node2vec. $AP = 0.04194$}
   \label{ROC_untrained}
  \end{figure}

@@

  \subsection{F-score}
  \begin{table}[H]
  \begin{tabular}{l|l}
  \textbf{Matcher} & \textbf{$F_1$-score}\\
  \hline
  Alternative & 0.4244\\
  Bidirectional & 0.4245\\
  Untrained & 0.4245\\
  Generic & 0.4245\\
  \textbf{AML} & \textbf{0.94}\\ %http://disi.unitn.it/~pavel/om2015/
  %papers/om2015_proceedings.pdf#page=125
  \end{tabular}
  \caption[$F_1$ mice]{The $F_1$-scores for the different matchers for the mice dataset}
  \label{fscores}
  \end{table}
  \subsection{Jaccard}
  TBD
  \subsection{Examples to illustrate the differences}
  TBD

@@

 \subsection{Discussion}
  The system underperforms on the provided data. This can have one or more of the following four potential causes:
  \begin{enumerate}
  \item The data breaks the considered algorithms.
  \item There are bugs in the developed system unrelated to the algorithms.
  \item The considered context extraction does not work.
  \item The considered algorithms are not suited for Ontology matching.
  \end{enumerate}

  I will investigate all four of these causes to see which is the most likely. If potential cause one is the case, the study is invalid and should be repeated on one or more different data sets. If either potential cause two or three is the actual cause, the study is invalid and the results should not be published until the system is fixed and the results do not change. If it is the case that none of these three potential causes is the actual cause, by elimination the fourth potential cause must be the actual cause. In that case the study is valid and it will be possible to draw the final conclusion.

  \subsubsection{The data}
  If the data set is the cause of the underperformance, switching to another data set will improve performance over the baseline. Possible reasons the data set causes underperformance include the data set being too small, labels that are not useful or the data set having a structure that does not work with the algorithm. For example, the pre-trained \emph{Word2vec} model is expected to work better on a data set that has commonly used words as labels. %Aanpassen als ik 3e dataset heb.
  \paragraph{}
 The algorithm has been run on multiple data sets which are different. Despite that there is no significant difference in performance. For example, compare the Average precision for the medical dataset with the anatomy dataset. The %TODO AP is between baseline en AML for both?
 So the data does not cause the underperformance of the system.

 %Ik heb bewust gekozen voor kleine data zodat het te vergelijken was met andere matchers. Want iedereen in OM gebruikt kleine datasets.
 %Deepwalk paper ook kleine data
 %Misschien heb ik te weinig data gebruikt maar er is geen grote dataset met ground truth beschikbaar.
 %Further research: grote dataset maken door LOD te pakken, 10% weg te gooien en kijken of je dat reconstruct. 
  \subsubsection{The system}
  % Sectie maken waar ik het systeem beschrijf
  If any of the steps in the software system contains an error, the whole system would fail. This could cause all algorithms to learn badly or the results to be misinterpreted. The system consists of a data loader, preprocessor, context extractor, the algorithm, the matcher and multiple visualizers. If all of these systems work properly, the system is not the reason for the underperformance.

  \paragraph{Data loading}
  \paragraph{Preprocessing}
  The preprocessing works, as described in Section \ref{preprocessing}.  The matcher is a simple KD-tree that finds the nearest neighbours of every node in the opposing Ontology. This is unlikely to contain errors.
  \paragraph{Matcher}
  \paragraph{Statistics and visualisation}
  Since the visualizers work in parallel, errors in them would not cascade to the others, so they are all faulty or none of them are.
  \paragraph{}
  Since every part works, the system is not faulty. %TODO kan beter

  Secondly, all steps have been replicated by another piece of software that does the data loading, preprocessing, context extraction and the algorithm. The results of that system are titled "alternative DeepWalk" in the results Section. As system has been used in other projects and is written by someone else, it can be concluded that it works. This is more proof that the system indeed works as intended.

  \subsubsection{Context extraction}
  There are different context extractors for some of the different algorithms. I will research every one: the sentence generator of DeepWalk, the context extractor for the graph-based models and the context extractor for the pre-trained model. If all three work well, the context extractors are not the cause of the underperformance.
  \paragraph{}
  The context extractor for DeepWalk works as generates sentences as described in Section \ref{sentences}. Since the sentences are generated properly and DeepWalk only requires sentences, the context extraction for DeepWalk works.
  \paragraph{}
  For the Node2vec algorithms, the context extraction is more advanced. All edges are extracted from the Ontology using Jena. Then, for every node the context is decided as every node it has an edge with. In the case of the bidirectional algorithm, both outgoing and ingoing edges count as being connected, whereas in the monodirectional algorithm only outgoing edges count as the connectedness. For the algorithms that also use the edge labels for context, double the context size is expected.
  \paragraph{}
  The context extraction of the pre-trained Word2vec consists of splitting up every label into multiple words which can be looked up. For example "Adrenal vein" can be split up into "Adrenal" and "vein".
  The pre-trained model does not use any other form of context integration.
  \paragraph{}
  First, I obtained the number of edges from VOWLview\cite{vowlview}, an Ontology graphing program. This was necessary since the creators of the data did not share how many edges were in the database. With the actual number of edges, obtained, it is possible to compare them with the number of edges found. If these match, the context extraction works.
  \begin{table}[H]
  \begin{tabular}{l|ll|ll}
  & \multicolumn{2}{c}{\#edges mice} & \multicolumn{2}{c|}{\#edges humans}\\
  Algorithm & expected & actual & expected & actual\\
  \hline
  \textbf{Truth}\cite{mice_ontology} & \multicolumn{2}{c|}{\textbf{1810}} & \multicolumn{2}{c}{\textbf{3780}} \\
  Monodirectional & & & &\\
  Bidirectional & & & &\\
  Bidirectional \& edges & & & &\\
  \end{tabular}
  \caption[Edge comparison]{The number of edges compared to show that edge parsing was successful.}
  \label{edgecounts}
  \end{table}
  Since the expected number of edges and actual number of edges match, we can conclude that the context extraction works.

  \subsubsection{The algorithm}
  At the beginning of this section, I reasoned that there are four possible causes for the underperformance of the system. The first three being bad data, bad code and bad context extraction. I have shown that all three are very unlikely to be the cause of the underperformance. Since those three possibilities have been excluded, the most likely conclusion is last remaining possibility: the set of distributed embedding algorithms do not work well on Ontology data.

  % Uit mijn onderzoek blijkt dat McCallum's algoritme niet werkt op SW. Als ik terugkijk naar zijn keynote, is dat wel logisch, want in zijn voorbeeld heeft hij een dataset gegeven waar de KBs toevallig dezelfde Named Entities hebben (perfect zijn). In de echte wereld is dit met de meeste data niet zo, helemaal in het SW omdat veel ambiguiteit door auatomatscih maken.

 % Plaatje van mccallum matrix. Kijk, Steve heet Steven in alle drie de KBs. Dit is in het echt dus niet zo.
 \subsection{Future research}

>>>>

 \usepackage[utf8]{inputenc}
 \usepackage[titletoc]{appendix}
 \usepackage{listings}
 \usepackage{amsmath}
 \usepackage{graphicx}
 \usepackage{float}
 \usepackage{caption}
 \usepackage[export]{adjustbox}
 \usepackage{url}
 \usepackage{subcaption}
 \usepackage{multirow}

 \title{Graphs of Mice and Men}
 %subtitle{Matching ontologies with distributed word embeddings}
 \author{Harmen Prins}

 \begin{document}
 \pagenumbering{gobble}
 \maketitle

 \makebox[\textwidth][c]{
 \includegraphics[width=1.35\textwidth]{plots/miceman}
 }\footnote{Credit: Sanna Dinh}
 \newpage

@@

 \section*{Summary}
 %TODO Definitions
 %TODO Word index
 %TODO Fix hoofdletters (bv ontology, kb)
 %TODO spelling (database dataset)
 %TODO volgorde bieb (APA?)
 %TODO Results interpretation: uitleg waarom hoger en lager
 %TODO Plaatje VOWL
 %TODO Verbeteringen discussieren
 %TODO 
 \tableofcontents
 \newpage

 %Vragen
 % Hypothese waarom ik dat denk?
 % extra hypothese

@@

The Universal Schema uses two steps. Firstly, the system learns embeddings of entities and relations found in text and Knowledge Bases\cite{universalschema}, see Figure \ref{McCallum_matrix}. Secondly, these embeddings are then used to predict new relations for the knowledge bases. The system finds embeddings such that the embeddings of entities and relations that co-occur are highly similar, see Figure \ref{McCallum_matrix}.

@@

 \begin{figure}[H]
 \centering
 \includegraphics[width=0.8\textwidth]{plots/Skip-Gram}
 \caption[Skip-Gram Model]{The embedding of a row (in pink) is optimized to be close to its context embeddings (in purple) but far away from other embeddings (in red).}
 \label{Skip-Gram-img}
 \end{figure}

@@

 McCallum plans on using these embeddings to predict new intra-knowledge base relations. However, from the keynote it is clear that this technique should work with multiple Knowledge Bases as the Universal Schema is applied to a set of Knowledge Bases including Freebase, knowledge extracted from text and the TAC Knowledge Bases Population Track Dataset. This means that inter-knowledge base relations can also be predicted using the Word Embedding Tensor Factorisation technique.

@@

 \newpage
 \section{Method} 
 This section contains the description of the matching system and experimental setup. It consists of four parts. Firstly, it describes the idea and challenges of implementing the system. Secondly, it describes the data used to test the system. The third part describes the whole system, including all different implementations of the algorithm and a system check to ensure valid results. The fourth and last part describes the evaluation criteria.

@@

 \subsection{System check}
 To ensure the results are valid, I ran a system check. The check is designed to detect the following conditions.
  \begin{enumerate}
  \item The data breaks the considered algorithms.
  \item There are bugs in the developed system unrelated to the algorithms.
  \item The considered context extraction does not work.
  \end{enumerate}

  I will investigate all three to ensure they cannot be the cause of bad results and as a sanity check to prevent confirmation bias.
  If potential cause one is the case, the study is invalid and should be repeated on one or more different data sets. If either potential cause two or three is the actual cause, the study is invalid and the results should not be published until the system is fixed and the results do not change. If it is the case that none of these three potential causes is the possible, the results are valid, the results reflect the performance of the algorithm and valid conclusions can be drawn from this study.

  \subsubsection{The data}
  If the data set is broken, switching to another data set will substantially change performance. Of course, different data sets are inherently unequal in their difficulty. Therefore I will check the performance relative to the baseline and the best known algorithm. If it performs similarly relative to those references, it can be concluded that the data works as intended.

  Possible reasons for the data causing bad results include the data set being too small, labels that are not useful or the data set having a structure that does not work with the algorithm. For example, the pre-trained \emph{Word2vec} model is expected to work better on a data set that has commonly used words as labels. %TODO sowieso aanpassen maar ook aanpassen als ik 3e dataset heb.
  \paragraph{}
 The algorithm has been run on multiple data sets which are different. Despite that there is no significant difference in performance. For example, compare the Average precision for the medical dataset with the anatomy dataset. The [...] %TODO AP is between baseline en AML for both?
 So the data does not cause the underperformance of the system.

 %Ik heb bewust gekozen voor kleine data zodat het te vergelijken was met andere matchers. Want iedereen in OM gebruikt kleine datasets.
 %Deepwalk paper ook kleine data
 %Misschien heb ik te weinig data gebruikt maar er is geen grote dataset met ground truth beschikbaar.
 %Further research: grote dataset maken door LOD te pakken, 10% weg te gooien en kijken of je dat reconstruct. 
  \subsubsection{The system}
  Since the system parts are connected in sequence, if any of the steps in the software system contains an error, the whole system fails. This could cause all algorithms to learn badly or the results to be misinterpreted. The system consists of a data loader, preprocessor, context extractor, the algorithm, the matcher and multiple visualizers. If all of these systems work properly, the system is not the reason for the underperformance. I will analyse every part except for the context extractor, which will be analysed in the next section.

  \paragraph{Preprocessing}
%  The preprocessing works as described in Section \ref{preprocessing}. 
  \paragraph{Matcher}The matcher is a simple KD-tree that finds the nearest neighbours of every node in the opposing Ontology. This is unlikely to contain errors.
  \paragraph{Data loading}
  Since the preprocessing and context extraction works, we can conclude that the data is also loaded properly.
  \paragraph{Statistics and visualisation}
  Since the visualizers work in parallel, errors in them would not cascade to the others, so they are all faulty or none of them are.
  \paragraph{}
  Since every part works, the system is not faulty. %TODO kan beter

  Secondly, as an extra measure, the following steps have been replicated by another piece of software: the data loader, preprocessor, context extractor and the algorithm. The results of that system are titled "alternative DeepWalk" in the results Section. As this system has been used in other projects and is written by someone else, if the results match the ones from this study, the system from this study works.

  \subsubsection{Context extraction}
  There are different context extractors for some of the different algorithms. I will research every one: the sentence generator of DeepWalk, the context extractor for the graph-based models and the context extractor for the pre-trained model. If all three work well, the context extractors are not the cause of the underperformance.
  \paragraph{}
  The context extractor for DeepWalk works as generates sentences as described in Section \ref{sentences}. Since the sentences are generated properly and DeepWalk only requires sentences, the context extraction for DeepWalk works.
  \paragraph{}
  For the Node2vec algorithms, the context extraction is more advanced. All edges are extracted from the Ontology using Jena. Then, for every node the context is decided as every node it has an edge with. In the case of the bidirectional algorithm, both outgoing and ingoing edges count as being connected, whereas in the monodirectional algorithm only outgoing edges count as the connectedness. For the algorithms that also use the edge labels for context, double the context size is expected.
  \paragraph{}
  The context extraction of the pre-trained Word2vec consists of splitting up every label into multiple words which can be looked up. For example "Adrenal vein" can be split up into "Adrenal" and "vein".
  The pre-trained model does not use any other form of context integration.
  \paragraph{}
  First, I obtained the number of edges from VOWLview\cite{vowlview}, an Ontology graphing program, which looks like Figure \ref{vowlfig}. This was necessary since the creators of the data did not share how many edges were in the database. With the actual number of edges, obtained, it is possible to compare them with the number of edges found. If these match, the context extraction works.

  \begin{figure}
  \includegraphics[width=0.7\textwidth]{vowlview}
  \caption[]{}
  \label{vowlfig}
  \end{figure}

  \begin{table}[H]
  \caption[Edge comparison]{The number of edges compared to show that edge parsing was successful.}
  \label{edgecounts}
  \begin{tabular}{l|ll|ll}  
  & \multicolumn{2}{c}{\#edges mice} & \multicolumn{2}{c|}{\#edges humans}\\
  Algorithm & expected & actual & expected & actual\\
  \hline
  \textbf{Truth*} & \multicolumn{2}{c|}{\textbf{1810}} & \multicolumn{2}{c}{\textbf{3780}} \\
  Monodirectional & 1810 & 1807 & 3780 & 3761\\
  Bidirectional & 3620 & 3614 & 7560 & 7522\\
  \end{tabular}
  \end{table}

  Since the expected number of edges and actual number of edges are very similar, we can conclude that the context extraction works. The difference can be explained by oddities in the VOWLview representation, as it contains edges that are not relevant to the ontology such as in Figure \ref{thing_edges}.

  \begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{plots/thing_edges}
  \caption[Addition edges example]{An example of two edges that VOWLview renders that are not relevant to ontology matching.}
  \label{thing_edges}
  \end{figure}

  \subsubsection{The algorithm}
  At the beginning of this section, I reasoned that there are three possible causes of system failure, namely, bad data, bad code and bad context extraction. I have shown that all three are unlikely to cause problems. Since those three possibilities have been excluded, it is certain that the results of this study are actual results.

 \subsubsection{Example: DeepWalk sentences} \label{sentences}

 \newpage
 \subsection{Evaluation}
 The goal of the research is to find an ontology alignment algorithm $A$ and prove that it performs better than current techniques. However, as current techniques may combine many different algorithms and sources of information, maybe such a comparison is not fair, nor is a comparison with individual algorithms as they may be optimised for being combined. So, instead we may want to see if performance is improved when adding $A$ to an ensemble of algorithms $E=(A_1,..,A_n)$.
 \subsubsection{Evaluation methods} \label{EvaluationMethods}
 The evaluation should be done using a performance measure $P(Al,T)$ that takes the alignment an algorithm produces given an ontology and the ground truth. If both the alignment and truth are considered sets of alignments, i.e. $Al=\{a_1,..,a_n\}$ and $T=\{a'_1,..,a'_m\}$, then the True Positives $TP=\{a|a\in Al, a\in T\}$, False Positives $FP=\{a|a\in Al, a\notin T\}$ and False Negatives $FN=\{a|a\in T, a\notin Al\}$ determine the performance of the alignment.

 \paragraph{Jaccard similarity}
 The True Negatives do not matter, as there are extremely many, and the goal of ontology matching is to find True Positives. If we only care about True Positives, the Jaccard similarity is a prime candidate for the performance measure.

 The Jaccard similarity is calculated as follows
 \[
 J = \frac{TP}{TP + FP + FN}
 \]
 i.e. the fraction of the true positives over the sum of the true positives and mistakes.
 \paragraph{}
 The Jaccard similarity is a number between 0 and 1, with a higher number being better. Therefore if we compare two alignments, the one which is most similar to the truth, i.e. has a higher Jaccard similarity, is the better one.
 \paragraph{}
 However, if we want to find out if an algorithm improves an ensemble, we calculate the improvement as follows:
 \[
 I = J_{E\cup \{A\}} - J_E
 \]
 where $J_E$ is the Jaccard coefficient of an ensemble $E$.
 To see if an algorithm is useful to an ensemble, the improvement score $I$ has to be \emph{significantly} higher than zero. To check if a score is significant, a statistical significance test will have to be carried out, which works as follows: generate $N$ solutions randomly and score them. Then score the method you want to investigate. If the score is in the top p\%, it is significant, otherwise it is not. In this case the solutions are $E\cup \{R\}$, where $R$ is an algorithm that generates random alignments\cite{fisher1925statistical}.
 \paragraph{}
 It is in principle possible to weigh False Positives and False Negatives differently, but this is not done in practice. To make the results of this study easily comparable to others, equal weights will be used.

 % Comparing the results. We want to compare to a baseline to ensure proper interpretation of the results. However, to test the hypothesis it is also required to compare the results to the best scoring algorithm on the same data set.

@@

 %TODO F-pieken aanwijzen. Dan confidence vs F-measure bespreken in interpretation.
 % Wat is de threshold van AML?
 % Extra rij met baseline literal string matcher
 \subsection{Precision versus recall}
  \subsubsection{Mice and men data}
  \begin{figure}[H]
   \centering
   \includegraphics[width=\textwidth]{plots/untrained_ROC}
   \caption[Precision-recall curve untrained mice]{The precision and recall trade-off for the results of the untrained Node2vec. $AP = 0.04194$}
   \label{ROC_untrained}
  \end{figure}

@@

  \subsection{F-score}
  \begin{table}[H]
  \caption[$F_1$ mice]{The $F_1$-scores for the different matchers for the mice dataset compared to the result of AML at OAEI 2015 \cite{oaei2015}}
  \label{fscores}
  \begin{tabular}{l|ll}
  \multirow{2}{*}{\textbf{Matcher}} & \multicolumn{2}{c}{\textbf{$F_1$-score}} \\
  & Anatomy & Medical\\
  \hline
  Alternative & 0.6372 & 0.2494 \\
  Bidirectional & 0.8432 & 0.4946 \\
  Label match + Random & 0.6926 & 0.3875 \\
  Generic & 0.6372 & 0.2419 \\
  \textbf{AML} & \textbf{0.94} & \textbf{0.81} \\ %http://disi.unitn.it/~pavel/om2015/
  %papers/om2015_proceedings.pdf#page=125
  \end{tabular}
  \end{table}
  %\subsection{Jaccard}
  %TBD
  \subsection{Examples to illustrate the differences}
  TBD

@@

 \subsection{Discussion}
 %TODO gooi weg wat niet meer waar is
  This study shows that the algorithm of McCallum et al as shown in \cite{mccallumweblecture} does not help improve the results of ontology alignment over the straightforward baseline of simply pairing labels based on their syntactic similarity in the area of Ontology Matching.

  The results show that one assumption that was made by the developers of the Universal Schema was incorrect, namely the assumption that when combining knowledge bases matching labels refer to the same entity and vice versa. For example, Bill Gates is called Bill Gates in FreeBase as well as retrieved from unstructured text. In reality, there may be multiple entities named Bill Gates and the same entity may be labelled differently.

  This assumption will weaken further as an increasingly growing part of the Semantic Web is automatically generated and as such different labels can be assigned to the same entity. One of the goals of Ontology Matching is to link those differently labelled entities.

  %In de presentatie zegt hij ook dat hij niet gaat proberen dingen meteen op elkaar te matchen maar gewoon alles houdt zoals het gelezen is/in de KB staat. Toch haalt hij goede resultaten met rule discovery e.d.
 \subsection{Future research}
